The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-17 ms/ms.tex
Updates from Overleaf

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Circles are drawn for 5 and 0.1 PgC bins respectively, with the circle size proportional to the number of simulations falling in that bin. In each case the largest circle is centered at the default simulation.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.pdf}
\caption{needs caption}
\label{fig:violins}
\end{figure}
